A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-03 pilot-publication/manuscript.Rmd
Start adding results to manuscript

## Patient Participant Outcomes
A total of `r n.m30d.atls` ( `r p.m30d.atls`%) patients in the ATLS
arm had the primary outcome, compared to `r n.m30d.ptc` (
`r p.m30d.ptc`%) patients in the PTC arm, and `r n.m30d.control` (
`r p.m30d.control`%) patients in the standard care arm. The absolute risk
difference between the ATLS and PTC arm was `r arr.atls.ptc`% units
<!--(95% CI X - X)-->, between the ATLS and standard care arms 
`r arr.atls.control`% units <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r arr.ptc.control`% units <!--(95% CI X
-X)-->. The relative risk between the ATLS and PTC arm was 
`r rr.atls.ptc` <!--(95% CI X - X)-->, between the ATLS and standard care
arms `r rr.atls.control` <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r rr.ptc.control` <!--(95% CI X - X)-->.

>>>>

## Patient Participant Outcomes

```{r, echo = FALSE}
post.training.outcomes.table <- outcome.results.tables$ci.level.0.95[["Outcomes in all patients after training, by treatment arm"]]
```

After training, a total of `r n.m30d.atls` ( `r p.m30d.atls`%) patients in the ATLS
arm had the primary outcome, compared to `r n.m30d.ptc` (
`r p.m30d.ptc`%) patients in the PTC arm, and `r n.m30d.control` (
`r p.m30d.control`%) patients in the standard care arm. The absolute risk
difference between the ATLS and PTC arm was `r arr.atls.ptc`% units
<!--(95% CI X - X)-->, between the ATLS and standard care arms 
`r arr.atls.control`% units <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r arr.ptc.control`% units <!--(95% CI X
-X)-->. The relative risk between the ATLS and PTC arm was 
`r rr.atls.ptc` <!--(95% CI X - X)-->, between the ATLS and standard care
arms `r rr.atls.control` <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r rr.ptc.control` <!--(95% CI X - X)-->.
